---
title: "Title of Project"
author: "Student SID"
subtitle: "Project 1"
date: "University of Sydney | DATA1001 | January 2021"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

<br>

# Executive Summary

<br>

# Full Report

## Initial Data Analysis (IDA)

The Newtown property prices dataset comes from data scraped by [domain](www.domain.com.au) in June 2017. 

```{r}
# Read in the Newtown data
property = read.csv("http://www.maths.usyd.edu.au/u/UG/JM/DATA1001/r/current/data/NewtownJune2017.csv")
str(property)


## Quick snapshot
dim(property)
str(property)
```

<br>

## Research Questions (given)

### What was the average price of a property?

```{r, results = "hide"}
# all properties
mean(property$Sold)
median(property$Sold)
sd(property$Sold)
IQR(property$Sold)

# Just 2 bedroom properties
mean(property$Sold[property$Bedrooms=="2"])
median(property$Sold[property$Bedrooms=="2"])
sd(property$Sold[property$Bedrooms=="2"])
IQR(property$Sold[property$Bedrooms=="2"])
```

### Does the amount of carspots affect the price?

```{r, results = "hide"}
mean(property$Sold[property$Carspots=="0"])
mean(property$Sold[property$Carspots=="1"])
mean(property$Sold[property$Carspots=="2"])
```

###  What were the cheapest properties?

First, we could just sort by the sold price.

```{r}
# Sort all prices
sold = property$Sold
sort(sold)
```

It would nice to list the details about the cheapest properties. Try the following code.

```{r}
attach(property)   # The database is attached to the R search path, so variables in the database can be accessed by simply giving their names.
head(property[order(Sold), ][c(1, 6, 7)], 10)
```

### Assuming commission fees are around 2%, which agency earnt the most over that period? 

```{r}
# Example of extracting Agent sales
sum(property$Sold[property$Agent=="RayWhite"])*0.02
```


## Research Question (own)





