---
title: "Assign1"
author: "abcd"
date:   "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: cerulean
    keep_md: true
    toc: yes
    toc_float: true
    highlight: haddock
---

```{r, include = F}
library(stargazer)
library(car)
library(lmtest)
library(tidyverse)
```


```{r, include = F}
df = read.csv("assign1.csv")
```

# Q1
## a) [6 marks] What is the interpretation of the population parameters βK,βL, and βM?
## b) [2 marks] Estimate the econometric model (2) in R using the method of Ordi- nary Least Squares (OLS) and report the results. Do the signs of your estimated coefficients turn out as you expect? Why or why not?

```{r}
reg1 = lm(lnroutput ~ lnrmaterials + lnlabour + lnrcapital, data = df)
summary(reg1)
```

## c

### c-i) Constant returns to scale implies that a doubling of all factor inputs (K, L,and M) exactly doubles production. In terms of the model (2), this imposes the restriction (βK + βL + βM ) = 1

```{r}
linearHypothesis(reg1, "lnrmaterials + lnlabour + lnrcapital = 1")
qf(.95, 3, 1935)
```

### c-ii) [6 marks] Without using the car package in R, test the hypothesis of constant returns to scale, for model (2), at a 5% level of significance using an F-test.

$$
F =   {{(RSS_R −RSS_{UR})/M} \over {RSS_{UR} /(N − K − 1)}} ∼ F (M ,\  N − K − 1)
$$

```{r}
df$y_k = df$lnroutput - df$lnrcapital
df$l_k = df$lnlabour - df$lnrcapital
df$m_k = df$lnrmaterials - df$lnrcapital
reg2 = lm(y_k ~ l_k + m_k, data = df)
```


```{r}
summary(reg1)
# 0.4524  on 1936 degrees of freedom # 3 and 1936 DF
summary(reg2) 
# 0.4642 on 1937 degrees of freedom #  2 and 1937 DF
n = 1937; k =2
F_value_q1 = ((0.4642 - 0.4524)/k) / ((0.4524)/(n-k-1))
F_value_q1

qf(.95, 2, 1937)

# 
# 0.9368/2 / ((1-0.9368)/(n-k-1))
```

 
H0: the two models are different.
F_value = `r F_value_q1`, which is larger than `r qf(.95, 3, 1936)`, hence we reject H0. The two models are not different, which implies that ($\beta_K$ + $\beta_L$ + $\beta_M$) = 1.

### c-iii) [8 marks] Without using the car package in R, test the hypothesis of constant returns to scale, for model (2), at a 5% level of significance using a t-test.

$$VAR(aX+bY +cZ)=a^2 VAR(X)+b^2 VAR(Y)+c^2VAR(Z) +2ab COV(X,Y)+2bc COV(Y,Z)+2ac COV(X,Z)$$

```{r}
# klm
vcov(reg1)
reg1; reg1$coefficients[2]
upper = (reg1$coefficients[2] + reg1$coefficients[3] + reg1$coefficients[4] - 1)
lower = vcov(reg1)[2,2] + vcov(reg1)[3,3] + vcov(reg1)[4,4] + 
        2*vcov(reg1)[2,3] + 2*vcov(reg1)[2,4] + 2*vcov(reg1)[3,4]
upper/sqrt(lower) 

# cat("t-value is: ", )
# 10.15943^2 # [1] 103.214
```


## d) [6 marks] Test the hypothesis that model (2) is correctly specified using the Ram- sey RESET test, at the 5% level, using both the squares and the cubes of the fitted values. What is your conclusion?

```{r}
resettest(reg1, power=2:3, type="fitted")
```

## e) Suppose this alternative model has been estimated using the data in assign1.csv and a value of R2 = 0.8749 was obtained. Consider the following statement: “Given the sample of data, the econometric model (2) is preferred to the alternative econometric model (3) because it has a larger R2.” Do you agree with this statement. Why or why not? 

---

# Question 2 [Total 40 marks] Consider the following extended version of model (1):

## question 2 a)
```{r}
assign1 <- read.csv("assign1.csv")
meanlnrcapital <- mean(assign1$lnrcapital)
meanlnrlabour  <- mean(assign1$lnlabour)
meanlnrmatrerials <- mean(assign1$lnrmaterials)
meanout <- mean(assign1$lnroutput)
print(meanlnrcapital)
print(meanlnrlabour)
print(meanlnrmatrerials)

```


```{r}
# 
# assign1
reg4 = lm(lnroutput ~ . + I(lnrcapital^2) + I(lnlabour^2) + I(lnrmaterials^2) +
            lnrcapital:lnlabour + lnlabour:lnrmaterials + lnrmaterials:lnrcapital -
            sector1 - firm, data = assign1)
summary(reg4)
```

## question 2 b)your estimates for model (4) calculate the following estimated elasticities, evaluated at the sample means:

```{r}
# reg4 is log-log regression
reg4$coefficients['lnrcapital']
reg4$coefficients['lnlabour']
reg4$coefficients['lnrmaterials']
```

$$
elasticity = {\partial output\over}
$$

## question 2 c)

# the real level of output is increasing over time.

```{r}
summary(reg4)
linearHypothesis(reg4, "year = 0")
```


#--------------------------------------------
# question 2 d)

```{r}
resettest(reg4, power=2:3, type="fitted")
```

#--------------------------------------------
# question 2 e)

```{r}

```


#--------------------------------------------
# question 2 f)

```{r}
linearHypothesis(reg4, "lnrmaterials + lnlabour + lnrcapital = 1")

linearHypothesis(reg4, "2*I(lnrcapital^2) + lnrcapital:lnlabour + lnrmaterials:lnrcapital = 0")
linearHypothesis(reg4, "2*I(lnlabour^2)   + lnrcapital:lnlabour + lnrmaterials:lnlabour   = 0")
linearHypothesis(reg4, "2*I(lnrmaterials^2) + lnrmaterials:lnrcapital + lnrmaterials:lnlabour = 0")

summary(reg4)
# ....
# reg4$coefficients
 
```

#--------------------------------------------
# question 2 g)

```{r}
linearHypothesis(reg4, "sector2 + sector3 +
                 sector4 + sector5 + sector6 + sector7 + sector8 = 0")
# F = 4.1249
qf(.95, 7, length(assign1))
```
 